%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% This is a modified ONE COLUMN version of
% the following template:
% 
% Deedy - One Page Two Column Resume
% LaTeX Template
% Version 1.1 (30/4/2014)
%
% Original author:
% Debarghya Das (http://debarghyadas.com)
%
% Original repository:
% https://github.com/deedydas/Deedy-Resume
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% 
% TODO:
% 1. Integrate biber/bibtex for article citation under publications.
% 2. Figure out a smoother way for the document to flow onto the next page.
% 3. Add styling information for a "Projects/Hacks" section.
% 4. Add location/address information
% 5. Merge OpenFont and MacFonts as a single sty with options.
% 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% CHANGELOG:
% v1.1:
% 1. Fixed several compilation bugs with \renewcommand
% 2. Got Open-source fonts (Windows/Linux support)
% 3. Added Last Updated
% 4. Move Title styling into .sty
% 5. Commented .sty file.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Known Issues:
% 1. Overflows onto second page if any column's contents are more than the
% vertical limit
% 2. Hacky space on the first bullet point on the second column.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\documentclass[]{deedy-resume-openfont}


\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\namesection{Martin}{Ethier}{
\href{mailto:methier@edu.uwaterloo.ca}{methier@edu.uwaterloo.ca} |
(705) 303-8890 |
\urlstyle{same}\href{https://www.linkedin.com/in/ethiermartin/}{linkedin.com/in/ethiermartin} |
\urlstyle{same}\href{https://github.com/MartinEthier}{github.com/MartinEthier}
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Information column
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\sectionsep
\sectionsep
\descript{January 19th 2019}
\sectionsep
\sectionsep
\location{Clearpath Robotics Inc \\ Divisional Office \\ Kitchener, ON \\ 1425 Strasburg Road, Unit 2A \\ N2R 1H2}

\sectionsep

\sectionsep

Dear recruiter,

\sectionsep

\sectionsep

My name is Martin Ethier and I am in the Mechatronics Engineering program at the University of Waterloo. It is my interest in becoming an embedded systems developer that has led me to apply for this job. I believe that I have the skill set necessary to complete this job effectively. 

\sectionsep
I have plenty of C++ object oriented programming experience from taking multiple C++ courses to contributing to the computer vision code base for the Waterloo Aerial Robotics Team. These C++ courses have allowed me to cover many data structures including linked lists, stacks, queues, and trees. I also have Python experience writing automation scripts for medical radiation treatment planning software. Furthermore, developing computer vision code with Matlab has allowed me to develop very good image processing skills. I have also gained experience developing this code with version control through the use of Git.

\sectionsep
I am confident that my skills and experience are very well suited with what you are looking for. I'm sure that I would be able to have an impactful presence on your team. I know that I could bring great ideas to the team and I am not afraid of a challenge. If you wish to further discuss with me, you may contact me at the email or phone number listed above.
\sectionsep

\sectionsep
Sincerely,
\sectionsep

\sectionsep

\descript{Martin Ethier}

\end{document}  \documentclass[]{article}